---
title: "(W3) Data "
author: "Elisa Simon"
date: "8/30/2022"
output: github_document
bibliography: references.bib
---

# Swiss fertility, coffee and chocolate.

This report presents three data sets and their variables.


## Swiss fertility and socioeconomic indicators (swiss)

The _swiss_ data set in the R package 'datasets' provides information about fertility and socioeconomic indicators in different places in Switzerland in 1988.

Here are the first rows of the data set:

```{r, include=FALSE}
data(swiss)
```
```{r, echo = FALSE}
head(swiss)
```


### Data types

The table below describes the R and statistical data types of the variables:

|                  | **R data type** | **Statistical data type** |
|------------------|:---------------:|:-------------------------:|
| Fertility        |     numeric     |    quantitative discrete  |
| Agriculture      |     numeric     |    quantitative discrete  |
| Examination      |     numeric     |    quantitative discrete  |
| Education        |     numeric     |    quantitative discrete  |
| Catholic         |     numeric     |    quantitative discrete  |
| Infant Mortality |     numeric     |    quantitative discrete  |

_(Sadly, all the variables are of the same types)_


## Coffee and coding

This data set by @najelkotob_coffee_2018 contains data about coffee consumption and coding habits.

Here are the first rows of the data set:

```{r, include=FALSE}
library(readr)
CoffeeAndCodeLT2018_CoffeeAndCodeLT2018 <- read_csv("CoffeeAndCodeLT2018 - CoffeeAndCodeLT2018.csv")
```

```{r, echo = FALSE}
head(CoffeeAndCodeLT2018_CoffeeAndCodeLT2018)
```

### Data types

The table below describes the R and statistical data types of the variables:

|                       | **R data type** | **Statistical data type** |
|-----------------------|:---------------:|:-------------------------:|
| Coding hours          |     numeric     |   quantitative discrete   |
| Coffee cups per day   |     numeric     |   quantitative discrete   |
| Coffee time           |    character    |    qualitative nominal    |
| Coding without coffee |    character    |    qualitative nominal    |
| Coffee type           |    character    |    qualitative nominal    |
| Coffee solve bugs     |    character    |    qualitative ordinal    |
| Gender                |    character    |    qualitative nominal    |
| Country               |    character    |    qualitative nominal    |
| Age range             |    character    |    qualitative ordinal    |


## Chocolate

This data set is by @narejo_chocolate_2020 and contains data on chocolate.

Here are the first rows: 
```{r, include = FALSE}
library(readr)
chocolate <- read_csv("chocolate.csv")
```
```{r, echo=FALSE}
head(chocolate)
```


### Data types

The table below describes the R and statistical data types of the variables:

|                      | **R data type** | **Statistical data type** |
|----------------------|:---------------:|:-------------------------:|
| Company              |    character    |    qualitative nominal    |
| Specific bean origin |    character    |    qualitative nominal    |
| REF                  |     numeric     |   quantitative discrete   |
| Review date          |     numeric     |   quantitative discrete   |
| Cocoa percentage     |    character    |   quantitative discrete   |
| Company location     |    character    |    qualitative nominal    |
| Rating               |     numeric     |   quantitative discrete   |
| Bean type            |    character    |    qualitative nominal    |
| Broad bean origin    |    character    |    qualitative nominal    |


# References
