---
title: "(W4) Data Wrangling"
author: "Elisa Simon"
date: "8/31/2022"
output: github_document
bibliography: references.bib
---

# More chocolate

For the first part of this report, I choose the data set __chocolate__ (@narejo_chocolate_2020)

As the names of the variables are quite problematic, I used the `clean_names()` function (from the janitor package) to make them more R-friendly.

The aim of this data practical is to show that I can wrangle data. Therefore, a first step is to install the dplyr package.

Below are the first rows of the data set:

```{r, include=FALSE}
options(repos = list(CRAN="http://cran.rstudio.com/"))
install.packages("readr")
install.packages("janitor")
library(readr)
library(janitor)
chocolate <- read_csv("chocolate.csv")
clean_chocolate <- clean_names(chocolate)
head(chocolate)
install.packages("dplyr")
library(dplyr)
```

```{r, echo=FALSE}
head(clean_chocolate)
```

## Data preparation

### Filter the data by two variables

Here I choose to filter by the company location variable (Switzerland and Belgium).

```{r}
choose_chocolate <- clean_chocolate%>%
  filter(company_location%in%c("Switzerland", "Belgium"))
```

### Select a subset of columns

Then I decided to select three columns: cocoa percent, company location, and rating.

```{r}
choose_chocolate <- choose_chocolate %>%
  select(cocoa_percent, company_location, rating)
```

### Bonus: the lazy (but cleaner) way
```{r, eval = FALSE}
choose_chocolate <- choose_chocolate %>%
  filter(company_location%in%c("Switzerland", "Belgium")) %>%
  select(cocoa_percent, company_location, rating)
```

## Swiss and Belgian chocolate

### First few rows
```{r}
head(choose_chocolate)
```

### Last few rows
```{r}
tail(choose_chocolate)
```
### Structure
```{r}
str(choose_chocolate)
```

## swiss chocolate vs. belgian chocolate

I arranged the data by rating.

One can observe that Belgium appears 6 times and Switzerland 4 times in the top ten.
So far, it looks like belgian is better than swiss chocolate.

```{r, echo=FALSE}
chocolate_by_rating <- choose_chocolate %>% arrange(desc(rating))
chocolate_by_rating
```
### Results summarize

So... despite what one could predict from the top ten, it finally looks like the mean rating of swiss chocolate is higher than the belgian one.
```{r, echo=FALSE}
sum_chocolate <- choose_chocolate %>%
  group_by(company_location)%>%
  summarize(rate_mean = mean(rating))
head(sum_chocolate)
```

## Filter out NAs

NAs can be removed with the dplyr `filter(!is.na())` function.
But actually the `is.na()` shows that the data set includes no NA.
```{r, eval=FALSE}
nona_choose_chocolate <- choose_chocolate%>%
  filter(!is.na(company_location)) %>%
  filter(!is.na(cocoa_percent)) %>%
  filter(!is.na(rating))
  
is.na(choose_chocolate)
```

# Suicide and Happiness

For the second part of this report, I load two data sets :

+ the first one provides the annual number of deaths by cause in various countries and can be retrieved in @ritchie_suicide_2014.
+ the second one is about happiness and life satisfaction and can be retrieved in @ortiz-ospina_happiness_2013.

## Annual number of deaths by cause => suicide in 2005

```{r, include=FALSE}
annualnumberofdeaths <- read_csv("annual-number-of-deaths-by-cause.csv")
annualnumberofdeaths <- clean_names(annualnumberofdeaths)
suicide <- annualnumberofdeaths %>% 
  select(entity, year, suicide = deaths_self_harm_sex_both_age_all_ages_number) %>%
  filter(year == "2005")
suicide
```

```{r}
head(annualnumberofdeaths)
head(suicide)
```


## Happiness => Happiness in 2005
```{r, include=FALSE}
happiness_raw <- read_csv("happiness-cantril-ladder.csv")
happiness_raw <- clean_names(happiness_raw)
happiness_raw
happiness <- happiness_raw %>%
  select(entity, year, happiness = life_satisfaction_in_cantril_ladder_world_happiness_report_2022) %>%
  filter(year == "2005")
happiness
```

```{r}
head(happiness_raw)
head(happiness)
```

## Suicide and happiness

In here I used the `merge()` function to join the suicide and happiness data sets.
+ Only the countries (entity) present in both data sets are returned.
+ Only the variables entity, suicide, and happiness are selected.

```{r, include=FALSE}
suicide_happiness <- merge(suicide, happiness, by.x = "entity", by.y = "entity", sort = TRUE)
suicide_happiness %>% select(entity, suicide, happiness)
```
```{r}
head(suicide_happiness)
```

An interesting exploration of those variables would be to test the correlation of a higher score of happiness and a smaller number of death by suicide.

# References