---
title: "(W5) data visualization"
author: "Elisa Simon"
date: '2022-08-31'
output: github_document
bibliography: references.bib
---

# Marriage rate per 1000 habitants

(Dataset source: @ortiz-ospina_marriages_2020)

```{r, include=FALSE}
library(readr)
library(janitor)
library(dplyr)
library(tidyverse)
library(ggplot2)
marriage_rate_per_1000_inhabitants <- read_csv("marriage-rate-per-1000-inhabitants.csv")
marriage <- clean_names(marriage_rate_per_1000_inhabitants)
marriage <- marriage%>% rename(marriage_rate = crude_marriage_rate_per_1_000_inhabitants)
```

```{r, echo=FALSE}
head(marriage) 
```

## Description of content and data types

| Variable name     |          **Description**         | **R data type** |  **Statistical data** |
|-------------------|:--------------------------------:|:---------------:|:---------------------:|
| **Entity**        |      represents the country      |    character    |  qualitative nominale |
| **Code**          |       code for the country       |    character    |  qualitative nominale |
| **Year**          |               year               |     numeric     | quantitative discrete |
| **Marriage rate** | marriage rate per 1000 habitants |     numeric     | quantitative discrete |


## Wide/long transformation

The marriage data set is in long format.
```{r, echo=FALSE}
marriage_wide <- spread(marriage, year, marriage_rate)
head(marriage_wide)
```
## Data in tidy format ?

Data are tidy (in the original long format)
I additionally removed the 'code' column as it was redondant.

```{r, echo=FALSE}
marriage_clean <- marriage %>% select(!code)
head(marriage_clean)
```

## Separate and unite

The data set I choose is not really pertinent to do so. Therefore, I decided to first unit the entity and code variables and then to separate them again.

```{r, include=FALSE}
marriage_united <- unite(marriage, col = 'Codentity', c('entity', 'code'), sep = ", ", remove=TRUE)
marriage_separated <- separate(marriage_united, col = 'Codentity', c('entity', 'code'), sep = ", ", remove=TRUE)
```

```{r, echo=FALSE}
head(marriage_united)
head(marriage_separated)
```

## Create a plot

```{r, echo=TRUE}
ggplot(marriage_clean, aes(year, marriage_rate)) +
  geom_point() +
  geom_smooth(method=lm, color= "red", se=FALSE) +
  theme_bw() +
  coord_cartesian (ylim= c(0, 30))
```

# References

