---
title: "(W6) data visualization"
author: "Elisa Simon"
date: '2022-08-31'
output: github_document
bibliography: references.bib
---

# Of code and coffee

This data set contains data about coffee consumption and coding habits (source: @najelkotob_coffee_2018)
```{r, include=FALSE}
library(readr)
library(janitor)
library(dplyr)
library(tidyverse)
library(ggplot2)
CoffeeAndCode <- read_csv("CoffeeAndCodeLT2018 - CoffeeAndCodeLT2018.csv")
```

## Variables description
```{r, echo=FALSE}
head(CoffeeAndCode)
```


| Variable names      |                         **Description**                         | **R data type** | **Statistical data type** |
|---------------------|:---------------------------------------------------------------:|:---------------:|:-------------------------:|
| CodingHours         |                     time spend coding a day                     |     numeric     |   quantitative discrete   |
| CoffeeCupsPerDay    |                  number of cups of coffee a day                 |     numeric     |   quantitative discrete   |
| CoffeeTime          |       when the coffee is enjoyed (before or while coding)       |    character    |    qualitative nominal    |
| CodingWithoutCoffee | does it happens to the subject not to drink coffee while coding |    character    |    qualitative ordinal    |
| CoffeeType          |                           coffee brand                          |    character    |    qualitative nominal    |
| CoffeeSolveBugs     |                  does coffee help to solve bugs                 |    character    |    qualitative ordinal    |
| Gender              |                     gender of the individual                    |    character    |    qualitative nominal    |
| Country             |                             country                             |    character    |    qualitative nominal    |
| AgeRange            |                   age range of the individual                   |    character    |    qualitative ordinal    |


## Two questions

1. Is there a relationship between the time spend coding and the number of cups of coffee ?

2. Is there a relationship between the time spend coding and the coffee brand ?


## Visualization (1) : Coffee Cups and Coding Hours

Here I want to see whether there is a correlation between the variables CodingHours and CoffeeCupsPerDay.
Therefore, I used a __scatter plot__.

```{r, echo=FALSE}
scat_cups <- ggplot(CoffeeAndCode, aes(CodingHours, CoffeeCupsPerDay)) +
  geom_point() +
  geom_smooth(method=lm, color="red", se=TRUE) +
  theme_bw()

scat_cups
```

## Visualization (2): Coffee Brand and Coding Hours
```{r, echo=FALSE}
ggplot(CoffeeAndCode, aes(CoffeeType, CodingHours)) +
  geom_boxplot(fill = "red", alpha = 0.2) +
  theme_bw()
```

# References


