---
title: "(W7) data modeling"
author: "Elisa Simon"
date: '2022-08-31'
output: github_document
bibliography: references.bib
---

# Dataset: Suicide and Happiness

```{r, include=FALSE}
library(readr)
library(readxl)
library(janitor)
library(dplyr)
library(tidyverse)
library(ggplot2)

```

```{r, include=FALSE}
happiness_cantril_ladder <- read_csv("happiness-cantril-ladder.csv")
happiness_clean <- clean_names(happiness_cantril_ladder)
happiness <- happiness_clean %>% select(entity, year, score_happiness = life_satisfaction_in_cantril_ladder_world_happiness_report_2022) %>%
  filter(year == "2005")
annual_number_of_deaths_by_cause <- read_csv("annual-number-of-deaths-by-cause.csv")
annual_number_of_deaths_by_cause_clean <- clean_names(annual_number_of_deaths_by_cause)
suicide <- annual_number_of_deaths_by_cause_clean %>%
  select(entity, year, nb_suicide = deaths_self_harm_sex_both_age_all_ages_number) %>%
  filter(year == "2005")
suicide_happiness <- merge(happiness, suicide, by.x = "entity", by.y = "entity", sort= TRUE)
df <- suicide_happiness %>% select(entity, score_happiness, nb_suicide) %>%
  filter(!is.na(entity)) %>%
  filter(!is.na(score_happiness)) %>%
  filter(!is.na(nb_suicide))
```

## Data description

This dataset contains data found in @ortiz-ospina_happiness_2013 and @ritchie_suicide_2014.
The data set contains 101 observations of 3 variables.
```{r}
head(df)
```
Here's a brief description of the variables.

| Variable name       |        **Description**        | **R data type** |  **Statistical data** |
|---------------------|:-----------------------------:|:---------------:|:---------------------:|
| **entity**          |            country            |    character    |  qualitative nominal  |
| **nb_suicide**      | number of deaths by self-harm |     numeric     | quantitative continue |
| **score_happiness** |    life satisfaction score    |     numeric     | quantitative continue |

## Data visualization

So, I tried to visualize, but the problem is we should actually have kind of a suicide rate for each countries, rather than the actual number.
```{r, echo=FALSE}
ggplot(df, aes (score_happiness, nb_suicide)) +
  geom_point()
```

## Back to the data
So... I download a data set with the population of each country (source: [data.worldbank.org](https://data.worldbank.org/indicator/SP.POP.TOTL?end=2021&start=1960 #ref ) ), and do some merging stuff again.

```{r, include=FALSE}
API_SP_POP_TOTL_DS2_en_excel_v2_4473524 <- read_excel("API_SP.POP.TOTL_DS2_en_excel_v2_4473524.xls")
population <- clean_names(API_SP_POP_TOTL_DS2_en_excel_v2_4473524)
population

df_population <- population %>%
  select(entity = country_name, people = x2005)

df_shp_transitoire <- merge(df, df_population, by.x ="entity", by.y = "entity", sort = TRUE)
df_shp <- df_shp_transitoire %>%
  transmute(entity, score_happiness, suicide_per_100000_individuals = nb_suicide / people * 100000)
```
```{r, echo=FALSE}
head(df_shp)
```

## Let's try visuailzation again
Well, whether I've been doing something wrong, whether there is no appearent correlation between the score of life satisfaction and the number of suicide for 100'000 individuals.

```{r, echo=FALSE}
ggplot(df_shp, aes (suicide_per_100000_individuals, score_happiness)) +
  geom_point() +
  geom_smooth(method = lm, color="red", se=TRUE) +
  theme_bw()
```

# Hypothesis

H1: There is a negative correlation between the happiness score and the suicide rates.

## Statistical test

To know whether there is a correlation between the two variables, I run a Pearson's correlation test.

```{r, echo=FALSE}
cor.test(df_shp$score_happiness, df_shp$suicide_per_100000_individuals)
```

# Results
According to the Pearson's correlation test, the correlation coefficient is `0.05435654`, which is quite small by the way. Anyway, it may be "funny" that the correlation actually is not negative, which would suggest that having a higher life satisfaction results in a higher risk to die from suicide. 

However, as the p-value is `0.6088`, the results are not statistically significant.
So the hypothesis is not supported: we can't say that life satisfaction negatively impact deaths by self-harm.

# References


