---
title: "(W8) Linear Model"
author: "Elisa Simon"
date: '2022-08-31'
output: github_document
bibliography: references.bib
---

# Dataset: Student Alcohol Consumption

The data set contains information concerning alcohol consumption, sociodemographic status, and school-related topics (source: @ortiz_student_2016)

```{r, include=FALSE}
library(readr)
library(readxl)
library(janitor)
library(dplyr)
library(tidyverse)
library(ggplot2)
student_por <- read_csv("student-por.csv")
```

# Research questions and variables of interest

In this report, I aim to know whether there is a (causal) relationship between alcohol consumption on the weekdays and the number of failures one experiments in his study journey.

+ __H1__: There is a correlation between weekdays alcohol consumption and the number of failures.
+ __H2__: The number of failures can be predict based on weekday alcohol consumption.


## Variables of interest

__Explanatory variable__ : Dalc - weekdays alcohol consumption

+ numeric / quantitative discrete
+ (from 1 - very low, to 5 - very high)

__Response variable__ : failures - absolute number of past class failures

+ numeric / quantitative discrete


# Statistical investigations

## Are weekday alcohol consumption and number of failures correlated ?

First, we can look graphically if there's an evident correlation between the two variables

```{r, echo=FALSE}
ggplot(student_por, aes(Dalc, failures)) +
  geom_jitter() +
  theme_bw() +
  labs(x = "Weekdays alcohol consumption frequency (from 1 - very low to 5 - very high)", y = "Number of past class failures",
       title = "Weekdays alcohol consumption and number of failures")
  
```

Visually, it looks like there is a concentration of people that don't fail nor drink on weekdays. But, the correlation is not evident. Therefore, we should now run a correlation's test. As at least one of the variables is not continuous, we should use the Spearman's correlation test.

```{r, include=FALSE}
cor <- cor.test(student_por$Dalc, student_por$failures, method="spearman")
```
```{r, echo=FALSE}
cor
```

The Spearman's correlation test suggests that

+ There is a (weak) positive correlation between alcohol consumption and the number of failures (rho = 0.1088617)
+ The test is significant: the true correlation is not equal to 0 (p-value = 0.0055)

For now, we cannot say that the correlation imply a causation. 

### Linear regression failures ~ Dalc => Assumptions

__Independence of observations__: we don't care because we only have one explanatory and one response variables.

__Normality__ of the dependent variable can be checked with an histogram. 

```{r, echo=FALSE}
hist(student_por$failures)
```

Well, according to the histogram, we cannot use a Linear regression model. Let's run a shapiro test of normality just to be sure.

```{r, include=FALSE}
shapiro.test(student_por$failures)
```

The Shapiro-Wilk normality test also suggests a non normal distribution (p-value < 2.2e-16).

However, the __linearity__ or monotonicity of the relationship is also not evident, as we can see:

```{r, echo=FALSE}
plot(failures ~ Dalc, data=student_por)
```

So unfortunately, our data cannot be linearly modeled.

# References
